---
dataMaid: yes
title: COVID 24h - CODA19
subtitle: "Imputed Dataset"
date: 2021-02-02 18:35:36
output:
  pdf_document :
    latex_engine : xelatex
  html_document:
    df_print: paged
geometry: margin=2cm
documentclass: report
header-includes:
  - \renewcommand{\chaptername}{Part}
  - \newcommand{\fullline}{\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}}
  - \newcommand{\bminione}{\begin{minipage}{0.75 \textwidth}}
  - \newcommand{\bminitwo}{\begin{minipage}{0.25 \textwidth}}
  - \newcommand{\emini}{\end{minipage}}
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library("ggplot2")
library("pander")
```

```{r 'visualFunctions', echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
ggAggHist <- getFromNamespace("ggAggHist", "dataMaid")
ggAggBarplot <- getFromNamespace("ggAggBarplot", "dataMaid")
```

# Data report overview
The dataset examined has the following dimensions:


---------------------------------
Feature                    Result
------------------------ --------
Number of observations        866

Number of variables           145
---------------------------------




### Checks performed
The following variable checks were performed, depending on the data type of each variable:

---------------------------------------------------------------------------------------------------------------------------------------------------
&nbsp;                                                 character    factor    labelled   haven labelled   numeric    integer    logical     Date   
----------------------------------------------------- ----------- ---------- ---------- ---------------- ---------- ---------- --------- ----------
Identify miscoded missing values                       $\times$    $\times$   $\times$      $\times$      $\times$   $\times$             $\times$ 

Identify prefixed and suffixed whitespace              $\times$    $\times$   $\times$      $\times$                                               

Identify levels with < 6 obs.                          $\times$    $\times$   $\times$      $\times$                                               

Identify case issues                                   $\times$    $\times$   $\times$      $\times$                                               

Identify misclassified numeric or integer variables    $\times$    $\times$   $\times$      $\times$                                               

Identify outliers                                                                                         $\times$   $\times$             $\times$ 
---------------------------------------------------------------------------------------------------------------------------------------------------




Please note that all numerical values in the following have been rounded to 2 decimals.


# Summary table

-------------------------------------------------------------------------------------------------------------------------
&nbsp;                                          Variable class     # unique values   Missing observations  Any problems? 
----------------------------------------------- ---------------- ----------------- ---------------------- ---------------
[patient\_site\_uid]                            numeric                        866                 0.00 %                

[female]                                        numeric                          2                 0.00 %                

[male]                                          numeric                          2                 0.00 %                

[patient\_age]                                  numeric                         81                 0.00 %                

[death]                                         numeric                          2                 0.00 %                

[neuromuscular\_blocking\_agents]               numeric                          2                 0.00 %                

[x5\_alpha\_reductase\_inhibitors]              numeric                          2                 0.00 %                

[acetaminophene]                                numeric                          2                 0.00 %                

[adjuvants\_anesthesia]                         numeric                          2                 0.00 %    $\times$    

[adrenergic\_alpha\_1\_receptor\_antagonists]   numeric                          2                 0.00 %                

[adrenergic\_beta\_3\_receptor\_agonists]       numeric                          2                 0.00 %    $\times$    

[adrenergic\_beta\_antagonists]                 numeric                          2                 0.00 %                

[adrenergic\_uptake\_inhibitors]                numeric                          2                 0.00 %    $\times$    

[alcohol\_deterrents]                           numeric                          2                 0.00 %    $\times$    

[analgesics]                                    numeric                          2                 0.00 %                

[analgesics\_opioid]                            numeric                          2                 0.00 %                

[androgens]                                     numeric                          2                 0.00 %    $\times$    

[anesthetics\_local]                            numeric                          2                 0.00 %                

[anti\_anxiety\_agents]                         numeric                          2                 0.00 %    $\times$    

[anti\_arrhythmia\_agents]                      numeric                          2                 0.00 %                

[anti\_asthmatic\_agents]                       numeric                          2                 0.00 %                

[anti\_bacterial\_agents]                       numeric                          2                 0.00 %                

[anti\_infective\_agents\_local]                numeric                          2                 0.00 %                

[anti\_inflammatory\_agents]                    numeric                          2                 0.00 %                

[anti\_inflammatory\_agents\_non\_steroidal]    numeric                          2                 0.00 %                

[anti\_ulcer\_agents]                           numeric                          2                 0.00 %                

[anticholesteremic\_agents]                     numeric                          2                 0.00 %                

[anticoagulants]                                numeric                          2                 0.00 %                

[anticonvulsants]                               numeric                          2                 0.00 %                

[antidepressive\_agents]                        numeric                          2                 0.00 %                

[antidepressive\_agents\_tricyclic]             numeric                          2                 0.00 %    $\times$    

[antidiarrheals]                                numeric                          2                 0.00 %                

[antiemetics]                                   numeric                          2                 0.00 %                

[antifibrinolytic\_agents]                      numeric                          2                 0.00 %                

[antifungal\_agents]                            numeric                          2                 0.00 %    $\times$    

[antihypertensive\_agents]                      numeric                          2                 0.00 %                

[antimalarials]                                 numeric                          2                 0.00 %    $\times$    

[antimetabolites]                               numeric                          2                 0.00 %                

[antineoplastic\_agents\_hormonal]              numeric                          2                 0.00 %    $\times$    

[antiparkinson\_agents]                         numeric                          2                 0.00 %                

[antipruritics]                                 numeric                          2                 0.00 %                

[antipsychotic\_agents]                         numeric                          2                 0.00 %                

[antithyroid\_agents]                           numeric                          2                 0.00 %    $\times$    

[antitubercular\_agents]                        numeric                          2                 0.00 %    $\times$    

[antitussive\_agents]                           numeric                          2                 0.00 %                

[antiviral\_agents]                             numeric                          2                 0.00 %                

[benzodiazepines]                               numeric                          2                 0.00 %                

[bicarbonate]                                   numeric                          2                 0.00 %                

[bone\_density\_conservation\_agents]           numeric                          2                 0.00 %                

[bronchodilator\_agents]                        numeric                          2                 0.00 %                

[calcium\_regulating\_hormones\_and\_agents]    numeric                          2                 0.00 %                

[carbonic\_anhydrase\_inhibitors]               numeric                          2                 0.00 %                

[chelating\_agents]                             numeric                          2                 0.00 %                

[cholagogues\_and\_choleretics]                 numeric                          2                 0.00 %    $\times$    

[cholinesterase\_inhibitors]                    numeric                          2                 0.00 %                

[contraceptive\_agents\_hormonal]               numeric                          2                 0.00 %    $\times$    

[diuretics]                                     numeric                          2                 0.00 %                

[diuretics\_osmotic]                            numeric                          2                 0.00 %    $\times$    

[factor\_xa\_inhibitors]                        numeric                          2                 0.00 %                

[fibrinolytic\_agents]                          numeric                          2                 0.00 %    $\times$    

[gastrointestinal\_agents]                      numeric                          2                 0.00 %                

[glucocorticoids]                               numeric                          2                 0.00 %                

[gout\_suppressants]                            numeric                          2                 0.00 %                

[hematologic\_agents]                           numeric                          2                 0.00 %    $\times$    

[hemostatics]                                   numeric                          2                 0.00 %    $\times$    

[hiv\_medication]                               numeric                          2                 0.00 %                

[hypoglycemic\_agents]                          numeric                          2                 0.00 %                

[immunologic\_factors]                          numeric                          2                 0.00 %    $\times$    

[immunosuppressive\_agents]                     numeric                          2                 0.00 %                

[laxatives]                                     numeric                          2                 0.00 %                

[levothyroxine]                                 numeric                          2                 0.00 %                

[miotics]                                       numeric                          2                 0.00 %    $\times$    

[muscarinic\_antagonists]                       numeric                          2                 0.00 %                

[muscle\_relaxants\_central]                    numeric                          2                 0.00 %    $\times$    

[narcotic\_antagonists]                         numeric                          2                 0.00 %    $\times$    

[neuromuscular\_blocking\_agents\_2]            numeric                          2                 0.00 %                

[ophthalmic\_solutions]                         numeric                          2                 0.00 %                

[parasympatholytics]                            numeric                          2                 0.00 %                

[platelet\_aggregation\_inhibitors]             numeric                          2                 0.00 %                

[progestins]                                    numeric                          2                 0.00 %    $\times$    

[reverse\_transcriptase\_inhibitors]            numeric                          2                 0.00 %    $\times$    

[sedation]                                      numeric                          2                 0.00 %                

[serotonin\_5\_ht1\_receptor\_agonists]         numeric                          2                 0.00 %    $\times$    

[serotonin\_uptake\_inhibitors]                 numeric                          2                 0.00 %                

[sleep\_aids\_pharmaceutical]                   numeric                          2                 0.00 %                

[smoking\_cessation\_agents]                    numeric                          2                 0.00 %                

[vasodilator\_agents]                           numeric                          2                 0.00 %                

[vasopressors]                                  numeric                          2                 0.00 %                

[vitamin\_b\_complex]                           numeric                          2                 0.00 %                

[vitamins]                                      numeric                          2                 0.00 %                

[hemoglobin\_min]                               numeric                        103                 0.00 %    $\times$    

[hemoglobin\_max]                               numeric                         97                 0.00 %    $\times$    

[hemoglobin\_mean]                              numeric                        356                 0.00 %    $\times$    

[plt\_min]                                      numeric                        313                 0.00 %    $\times$    

[plt\_max]                                      numeric                        339                 0.00 %    $\times$    

[plt\_mean]                                     numeric                        588                 0.00 %    $\times$    

[wbc\_min]                                      numeric                        132                 0.00 %    $\times$    

[wbc\_max]                                      numeric                        184                 0.00 %    $\times$    

[wbc\_mean]                                     numeric                        398                 0.00 %    $\times$    

[sodium\_min]                                   numeric                         38                 0.00 %    $\times$    

[sodium\_max]                                   numeric                         36                 0.00 %    $\times$    

[sodium\_mean]                                  numeric                        179                 0.00 %    $\times$    

[potassium\_min]                                numeric                         32                 0.00 %    $\times$    

[potassium\_max]                                numeric                         34                 0.00 %    $\times$    

[potassium\_mean]                               numeric                        135                 0.00 %    $\times$    

[creatinine\_min]                               numeric                        175                 0.00 %    $\times$    

[creatinine\_max]                               numeric                        203                 0.00 %    $\times$    

[creatinine\_mean]                              numeric                        435                 0.00 %    $\times$    

[eos\_min]                                      numeric                         41                 0.00 %    $\times$    

[eos\_max]                                      numeric                         51                 0.00 %    $\times$    

[eos\_mean]                                     numeric                         45                 0.00 %    $\times$    

[lymph\_min]                                    numeric                        204                 0.00 %    $\times$    

[lymph\_max]                                    numeric                        231                 0.00 %    $\times$    

[lymph\_mean]                                   numeric                        225                 0.00 %    $\times$    

[neutrophil\_min]                               numeric                        428                 0.00 %    $\times$    

[neutrophil\_max]                               numeric                        489                 0.00 %    $\times$    

[neutrophil\_mean]                              numeric                        517                 0.00 %    $\times$    

[mono\_min]                                     numeric                        124                 0.00 %    $\times$    

[mono\_max]                                     numeric                        158                 0.00 %    $\times$    

[mono\_mean]                                    numeric                        138                 0.00 %    $\times$    

[baso\_min]                                     numeric                         14                 0.00 %                

[baso\_max]                                     numeric                         25                 0.00 %    $\times$    

[baso\_mean]                                    numeric                         19                 0.00 %    $\times$    

[sbp\_min]                                      numeric                         93                 0.00 %    $\times$    

[sbp\_max]                                      numeric                        117                 0.00 %    $\times$    

[sbp\_mean]                                     numeric                        637                 0.00 %    $\times$    

[dbp\_min]                                      numeric                         60                 0.00 %    $\times$    

[dbp\_max]                                      numeric                         76                 0.00 %    $\times$    

[dbp\_mean]                                     numeric                        555                 0.00 %    $\times$    

[temp\_min]                                     numeric                         36                 0.00 %    $\times$    

[temp\_max]                                     numeric                         51                 0.00 %    $\times$    

[temp\_mean]                                    numeric                        225                 0.00 %    $\times$    

[so2\_min]                                      numeric                         40                 0.00 %    $\times$    

[so2\_max]                                      numeric                         11                 0.00 %    $\times$    

[so2\_mean]                                     numeric                        451                 0.00 %    $\times$    

[rr\_min]                                       numeric                         17                 0.00 %    $\times$    

[rr\_max]                                       numeric                         27                 0.00 %    $\times$    

[rr\_mean]                                      numeric                        302                 0.00 %    $\times$    

[fio2\_min]                                     numeric                         39                 0.00 %    $\times$    

[fio2\_max]                                     numeric                         36                 0.00 %                

[fio2\_mean]                                    numeric                        257                 0.00 %                

[mv]                                            numeric                          2                 0.00 %                

[icu]                                           numeric                          2                 0.00 %                

[levelofcare]                                   numeric                          2                 0.00 %                

[wave]                                          numeric                          2                 0.00 %                
-------------------------------------------------------------------------------------------------------------------------




# Variable list
## patient\_site\_uid

\bminione

----------------------------------------------
Feature                                 Result
------------------------- --------------------
Variable type                          numeric

Number of missing obs.                 0 (0 %)

Number of unique values                    866

Median                                 5336432

1st and 3rd quartiles       830614.75; 5636957

Min. and max.                     720; 5682684
----------------------------------------------


\emini
\bminitwo
```{r 'Var-1-patient-site-uid', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 500000, 1000000, 
1500000, 2000000, 2500000, 3000000, 3500000, 4000000, 4500000, 
5000000, 5500000), xmax = c(500000, 1000000, 1500000, 2000000, 
2500000, 3000000, 3500000, 4000000, 4500000, 5000000, 5500000, 
6000000), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(120L, 
142L, 65L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 156L, 383L)), class = "data.frame", row.names = c(NA, 
-12L)), vnam = "patient_site_uid")
```

\emini




\fullline

## female

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-2-female', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(455L, 411L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "female")
```

\emini




\fullline

## male

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "1"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-3-male', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(411L, 455L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "male")
```

\emini




\fullline

## patient\_age

\bminione

-------------------------------------
Feature                        Result
------------------------- -----------
Variable type                 numeric

Number of missing obs.        0 (0 %)

Number of unique values            81

Median                             72

1st and 3rd quartiles       55.25; 84

Min. and max.                 19; 103
-------------------------------------


\emini
\bminitwo
```{r 'Var-4-patient-age', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(10L, 20L, 30L, 40L, 
50L, 60L, 70L, 80L, 90L, 100L), xmax = c(20L, 30L, 40L, 50L, 
60L, 70L, 80L, 90L, 100L, 110L), ymin = c(0, 0, 0, 0, 0, 0, 0, 
0, 0, 0), ymax = c(3L, 25L, 65L, 73L, 89L, 154L, 172L, 194L, 
88L, 3L)), class = "data.frame", row.names = c(NA, -10L)), vnam = "patient_age")
```

\emini




\fullline

## death

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-5-death', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(751L, 115L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "death")
```

\emini




\fullline

## neuromuscular\_blocking\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-6-neuromuscular-blocking-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(859L, 7L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "neuromuscular_blocking_agents")
```

\emini




\fullline

## x5\_alpha\_reductase\_inhibitors

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-7-x5-alpha-reductase-inhibitors', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(821L, 45L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "x5_alpha_reductase_inhibitors")
```

\emini




\fullline

## acetaminophene

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "1"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-8-acetaminophene', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(67L, 799L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "acetaminophene")
```

\emini




\fullline

## adjuvants\_anesthesia

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-9-adjuvants-anesthesia', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(861L, 5L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "adjuvants_anesthesia")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## adrenergic\_alpha\_1\_receptor\_antagonists

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-10-adrenergic-alpha-1-receptor-antagonists', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(768L, 98L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "adrenergic_alpha_1_receptor_antagonists")
```

\emini




\fullline

## adrenergic\_beta\_3\_receptor\_agonists

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-11-adrenergic-beta-3-receptor-agonists', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(861L, 5L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "adrenergic_beta_3_receptor_agonists")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## adrenergic\_beta\_antagonists

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-12-adrenergic-beta-antagonists', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(808L, 58L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "adrenergic_beta_antagonists")
```

\emini




\fullline

## adrenergic\_uptake\_inhibitors

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-13-adrenergic-uptake-inhibitors', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(865L, 1L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "adrenergic_uptake_inhibitors")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## alcohol\_deterrents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-14-alcohol-deterrents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(865L, 1L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "alcohol_deterrents")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## analgesics

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-15-analgesics', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(792L, 74L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "analgesics")
```

\emini




\fullline

## analgesics\_opioid

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-16-analgesics-opioid', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(510L, 356L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "analgesics_opioid")
```

\emini




\fullline

## androgens

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-17-androgens', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(864L, 2L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "androgens")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## anesthetics\_local

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-18-anesthetics-local', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(846L, 20L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "anesthetics_local")
```

\emini




\fullline

## anti\_anxiety\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-19-anti-anxiety-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(864L, 2L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "anti_anxiety_agents")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## anti\_arrhythmia\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-20-anti-arrhythmia-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(769L, 97L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "anti_arrhythmia_agents")
```

\emini




\fullline

## anti\_asthmatic\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-21-anti-asthmatic-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(855L, 11L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "anti_asthmatic_agents")
```

\emini




\fullline

## anti\_bacterial\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "1"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-22-anti-bacterial-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(331L, 535L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "anti_bacterial_agents")
```

\emini




\fullline

## anti\_infective\_agents\_local

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-23-anti-infective-agents-local', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(833L, 33L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "anti_infective_agents_local")
```

\emini




\fullline

## anti\_inflammatory\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-24-anti-inflammatory-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(844L, 22L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "anti_inflammatory_agents")
```

\emini




\fullline

## anti\_inflammatory\_agents\_non\_steroidal

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-25-anti-inflammatory-agents-non-steroidal', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(831L, 35L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "anti_inflammatory_agents_non_steroidal")
```

\emini




\fullline

## anti\_ulcer\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-26-anti-ulcer-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(435L, 431L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "anti_ulcer_agents")
```

\emini




\fullline

## anticholesteremic\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-27-anticholesteremic-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(600L, 266L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "anticholesteremic_agents")
```

\emini




\fullline

## anticoagulants

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "1"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-28-anticoagulants', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(184L, 682L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "anticoagulants")
```

\emini




\fullline

## anticonvulsants

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-29-anticonvulsants', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(813L, 53L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "anticonvulsants")
```

\emini




\fullline

## antidepressive\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-30-antidepressive-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(740L, 126L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "antidepressive_agents")
```

\emini




\fullline

## antidepressive\_agents\_tricyclic

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-31-antidepressive-agents-tricyclic', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(863L, 3L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "antidepressive_agents_tricyclic")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## antidiarrheals

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-32-antidiarrheals', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(851L, 15L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "antidiarrheals")
```

\emini




\fullline

## antiemetics

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-33-antiemetics', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(626L, 240L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "antiemetics")
```

\emini




\fullline

## antifibrinolytic\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-34-antifibrinolytic-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(860L, 6L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "antifibrinolytic_agents")
```

\emini




\fullline

## antifungal\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-35-antifungal-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(862L, 4L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "antifungal_agents")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## antihypertensive\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-36-antihypertensive-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(496L, 370L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "antihypertensive_agents")
```

\emini




\fullline

## antimalarials

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-37-antimalarials', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(864L, 2L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "antimalarials")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## antimetabolites

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-38-antimetabolites', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(828L, 38L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "antimetabolites")
```

\emini




\fullline

## antineoplastic\_agents\_hormonal

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-39-antineoplastic-agents-hormonal', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(862L, 4L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "antineoplastic_agents_hormonal")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## antiparkinson\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-40-antiparkinson-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(825L, 41L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "antiparkinson_agents")
```

\emini




\fullline

## antipruritics

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-41-antipruritics', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(856L, 10L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "antipruritics")
```

\emini




\fullline

## antipsychotic\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-42-antipsychotic-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(630L, 236L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "antipsychotic_agents")
```

\emini




\fullline

## antithyroid\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-43-antithyroid-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(865L, 1L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "antithyroid_agents")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## antitubercular\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-44-antitubercular-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(864L, 2L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "antitubercular_agents")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## antitussive\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-45-antitussive-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(854L, 12L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "antitussive_agents")
```

\emini




\fullline

## antiviral\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-46-antiviral-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(850L, 16L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "antiviral_agents")
```

\emini




\fullline

## benzodiazepines

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-47-benzodiazepines', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(479L, 387L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "benzodiazepines")
```

\emini




\fullline

## bicarbonate

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-48-bicarbonate', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(837L, 29L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "bicarbonate")
```

\emini




\fullline

## bone\_density\_conservation\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-49-bone-density-conservation-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(810L, 56L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "bone_density_conservation_agents")
```

\emini




\fullline

## bronchodilator\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-50-bronchodilator-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(610L, 256L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "bronchodilator_agents")
```

\emini




\fullline

## calcium\_regulating\_hormones\_and\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-51-calcium-regulating-hormones-and-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(607L, 259L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "calcium_regulating_hormones_and_agents")
```

\emini




\fullline

## carbonic\_anhydrase\_inhibitors

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-52-carbonic-anhydrase-inhibitors', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(854L, 12L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "carbonic_anhydrase_inhibitors")
```

\emini




\fullline

## chelating\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-53-chelating-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(849L, 17L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "chelating_agents")
```

\emini




\fullline

## cholagogues\_and\_choleretics

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-54-cholagogues-and-choleretics', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(863L, 3L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "cholagogues_and_choleretics")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## cholinesterase\_inhibitors

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-55-cholinesterase-inhibitors', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(826L, 40L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "cholinesterase_inhibitors")
```

\emini




\fullline

## contraceptive\_agents\_hormonal

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-56-contraceptive-agents-hormonal', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(864L, 2L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "contraceptive_agents_hormonal")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## diuretics

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-57-diuretics', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(663L, 203L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "diuretics")
```

\emini




\fullline

## diuretics\_osmotic

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-58-diuretics-osmotic', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(865L, 1L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "diuretics_osmotic")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## factor\_xa\_inhibitors

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-59-factor-xa-inhibitors', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(773L, 93L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "factor_xa_inhibitors")
```

\emini




\fullline

## fibrinolytic\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-60-fibrinolytic-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(865L, 1L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "fibrinolytic_agents")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## gastrointestinal\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-61-gastrointestinal-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(859L, 7L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "gastrointestinal_agents")
```

\emini




\fullline

## glucocorticoids

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-62-glucocorticoids', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(613L, 253L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "glucocorticoids")
```

\emini




\fullline

## gout\_suppressants

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-63-gout-suppressants', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(857L, 9L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "gout_suppressants")
```

\emini




\fullline

## hematologic\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-64-hematologic-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(862L, 4L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "hematologic_agents")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## hemostatics

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-65-hemostatics', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(863L, 3L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "hemostatics")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## hiv\_medication

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-66-hiv-medication', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(855L, 11L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "hiv_medication")
```

\emini




\fullline

## hypoglycemic\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-67-hypoglycemic-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(609L, 257L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "hypoglycemic_agents")
```

\emini




\fullline

## immunologic\_factors

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-68-immunologic-factors', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(865L, 1L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "immunologic_factors")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## immunosuppressive\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-69-immunosuppressive-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(841L, 25L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "immunosuppressive_agents")
```

\emini




\fullline

## laxatives

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "1"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-70-laxatives', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(309L, 557L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "laxatives")
```

\emini




\fullline

## levothyroxine

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-71-levothyroxine', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(712L, 154L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "levothyroxine")
```

\emini




\fullline

## miotics

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-72-miotics', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(864L, 2L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "miotics")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## muscarinic\_antagonists

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-73-muscarinic-antagonists', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(860L, 6L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "muscarinic_antagonists")
```

\emini




\fullline

## muscle\_relaxants\_central

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-74-muscle-relaxants-central', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(865L, 1L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "muscle_relaxants_central")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## narcotic\_antagonists

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-75-narcotic-antagonists', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(864L, 2L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "narcotic_antagonists")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## neuromuscular\_blocking\_agents\_2

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-76-neuromuscular-blocking-agents-2', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(839L, 27L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "neuromuscular_blocking_agents_2")
```

\emini




\fullline

## ophthalmic\_solutions

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-77-ophthalmic-solutions', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(837L, 29L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "ophthalmic_solutions")
```

\emini




\fullline

## parasympatholytics

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-78-parasympatholytics', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(859L, 7L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "parasympatholytics")
```

\emini




\fullline

## platelet\_aggregation\_inhibitors

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-79-platelet-aggregation-inhibitors', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(644L, 222L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "platelet_aggregation_inhibitors")
```

\emini




\fullline

## progestins

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-80-progestins', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(865L, 1L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "progestins")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## reverse\_transcriptase\_inhibitors

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-81-reverse-transcriptase-inhibitors', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(865L, 1L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "reverse_transcriptase_inhibitors")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## sedation

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-82-sedation', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(803L, 63L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "sedation")
```

\emini




\fullline

## serotonin\_5\_ht1\_receptor\_agonists

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-83-serotonin-5-ht1-receptor-agonists', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(864L, 2L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "serotonin_5_ht1_receptor_agonists")
```

\emini


- Note that the following levels have at most five observations: \"1\". 



\fullline

## serotonin\_uptake\_inhibitors

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-84-serotonin-uptake-inhibitors', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(802L, 64L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "serotonin_uptake_inhibitors")
```

\emini




\fullline

## sleep\_aids\_pharmaceutical

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-85-sleep-aids-pharmaceutical', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(846L, 20L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "sleep_aids_pharmaceutical")
```

\emini




\fullline

## smoking\_cessation\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-86-smoking-cessation-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(820L, 46L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "smoking_cessation_agents")
```

\emini




\fullline

## vasodilator\_agents

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-87-vasodilator-agents', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(815L, 51L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "vasodilator_agents")
```

\emini




\fullline

## vasopressors

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-88-vasopressors', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(747L, 119L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "vasopressors")
```

\emini




\fullline

## vitamin\_b\_complex

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-89-vitamin-b-complex', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(762L, 104L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "vitamin_b_complex")
```

\emini




\fullline

## vitamins

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-90-vitamins', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(463L, 403L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "vitamins")
```

\emini




\fullline

## hemoglobin\_min

\bminione

------------------------------------
Feature                       Result
------------------------- ----------
Variable type                numeric

Number of missing obs.       0 (0 %)

Number of unique values          103

Median                           119

1st and 3rd quartiles       104; 130

Min. and max.                41; 173
------------------------------------


\emini
\bminitwo
```{r 'Var-91-hemoglobin-min', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(40L, 50L, 60L, 70L, 
80L, 90L, 100L, 110L, 120L, 130L, 140L, 150L, 160L, 170L), xmax = c(50L, 
60L, 70L, 80L, 90L, 100L, 110L, 120L, 130L, 140L, 150L, 160L, 
170L, 180L), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0), ymax = c(1L, 3L, 18L, 29L, 44L, 80L, 123L, 183L, 182L, 129L, 
54L, 13L, 6L, 1L)), class = "data.frame", row.names = c(NA, -14L
)), vnam = "hemoglobin_min")
```

\emini


- Note that the following possible outlier values were detected: \"41\", \"153\", \"154\", \"155\", \"156\", \"157\", \"158\", \"159\", \"161\", \"162\" (4 additional values omitted). 



\fullline

## hemoglobin\_max

\bminione

------------------------------------
Feature                       Result
------------------------- ----------
Variable type                numeric

Number of missing obs.       0 (0 %)

Number of unique values           97

Median                           127

1st and 3rd quartiles       113; 138

Min. and max.                71; 178
------------------------------------


\emini
\bminitwo
```{r 'Var-92-hemoglobin-max', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(70L, 80L, 90L, 100L, 
110L, 120L, 130L, 140L, 150L, 160L, 170L), xmax = c(80L, 90L, 
100L, 110L, 120L, 130L, 140L, 150L, 160L, 170L, 180L), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(11L, 32L, 60L, 87L, 124L, 
193L, 190L, 95L, 51L, 14L, 9L)), class = "data.frame", row.names = c(NA, 
-11L)), vnam = "hemoglobin_max")
```

\emini


- Note that the following possible outlier values were detected: \"163\", \"164\", \"165\", \"167\", \"169\", \"170\", \"171\", \"172\", \"173\", \"176\" (1 additional values omitted). 



\fullline

## hemoglobin\_mean

\bminione

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                      numeric

Number of missing obs.             0 (0 %)

Number of unique values                356

Median                                 122

1st and 3rd quartiles       108.21; 133.64

Min. and max.                   61.71; 173
------------------------------------------


\emini
\bminitwo
```{r 'Var-93-hemoglobin-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(60L, 70L, 80L, 90L, 
100L, 110L, 120L, 130L, 140L, 150L, 160L, 170L), xmax = c(70L, 
80L, 90L, 100L, 110L, 120L, 130L, 140L, 150L, 160L, 170L, 180L
), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(2L, 
26L, 40L, 66L, 105L, 161L, 192L, 162L, 76L, 26L, 7L, 3L)), class = "data.frame", row.names = c(NA, 
-12L)), vnam = "hemoglobin_mean")
```

\emini


- Note that the following possible outlier values were detected: \"161\", \"161.33\", \"162\", \"162.5\", \"162.75\", \"163\", \"168.33\", \"170.33\", \"171.5\", \"173\". 



\fullline

## plt\_min

\bminione

------------------------------------
Feature                       Result
------------------------- ----------
Variable type                numeric

Number of missing obs.       0 (0 %)

Number of unique values          313

Median                           196

1st and 3rd quartiles       145; 261

Min. and max.                21; 941
------------------------------------


\emini
\bminitwo
```{r 'Var-94-plt-min', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 100, 200, 300, 400, 
500, 600, 700, 800, 900), xmax = c(100, 200, 300, 400, 500, 600, 
700, 800, 900, 1000), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), 
    ymax = c(70L, 379L, 293L, 93L, 25L, 3L, 2L, 0L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "plt_min")
```

\emini


- Note that the following possible outlier values were detected: \"21\", \"24\", \"26\", \"27\", \"32\", \"34\", \"35\", \"36\", \"37\", \"526\" (3 additional values omitted). 



\fullline

## plt\_max

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             339

Median                              227

1st and 3rd quartiles       170; 298.75

Min. and max.                  24; 1052
---------------------------------------


\emini
\bminitwo
```{r 'Var-95-plt-max', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 100, 200, 300, 400, 
500, 600, 700, 800, 900, 1000), xmax = c(100, 200, 300, 400, 
500, 600, 700, 800, 900, 1000, 1100), ymin = c(0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0), ymax = c(33L, 307L, 313L, 137L, 57L, 13L, 
4L, 1L, 0L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-11L)), vnam = "plt_max")
```

\emini


- Note that the following possible outlier values were detected: \"24\", \"26\", \"37\", \"44\", \"50\", \"58\", \"61\", \"62\", \"63\", \"608\" (3 additional values omitted). 



\fullline

## plt\_mean

\bminione

-----------------------------------------
Feature                            Result
------------------------- ---------------
Variable type                     numeric

Number of missing obs.            0 (0 %)

Number of unique values               588

Median                                208

1st and 3rd quartiles         158; 281.88

Min. and max.               23.86; 989.75
-----------------------------------------


\emini
\bminitwo
```{r 'Var-96-plt-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 100, 200, 300, 400, 
500, 600, 700, 800, 900), xmax = c(100, 200, 300, 400, 500, 600, 
700, 800, 900, 1000), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), 
    ymax = c(49L, 343L, 311L, 120L, 34L, 5L, 2L, 0L, 0L, 2L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "plt_mean")
```

\emini


- Note that the following possible outlier values were detected: \"23.86\", \"24\", \"33.75\", \"40.25\", \"43.5\", \"44.6\", \"47.33\", \"47.75\", \"48.4\", \"50\" (11 additional values omitted). 



\fullline

## wbc\_min

\bminione

------------------------------------
Feature                       Result
------------------------- ----------
Variable type                numeric

Number of missing obs.       0 (0 %)

Number of unique values          132

Median                           5.5

1st and 3rd quartiles       4.1; 7.5

Min. and max.                0; 46.1
------------------------------------


\emini
\bminitwo
```{r 'Var-97-wbc-min', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 5, 10, 15, 20, 25, 
30, 35, 40, 45), xmax = c(5, 10, 15, 20, 25, 30, 35, 40, 45, 
50), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(360L, 431L, 
59L, 10L, 4L, 1L, 0L, 0L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "wbc_min")
```

\emini


- Note that the following possible outlier values were detected: \"0\", \"0.7\", \"1\", \"1.2\", \"1.3\", \"1.5\", \"1.6\", \"1.8\", \"1.9\", \"17.8\" (6 additional values omitted). 



\fullline

## wbc\_max

\bminione

--------------------------------------
Feature                         Result
------------------------- ------------
Variable type                  numeric

Number of missing obs.         0 (0 %)

Number of unique values            184

Median                             7.4

1st and 3rd quartiles       5.4; 10.47

Min. and max.                1.3; 1000
--------------------------------------


\emini
\bminitwo
```{r 'Var-98-wbc-max', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 100, 200, 300, 400, 
500, 600, 700, 800, 900), xmax = c(100, 200, 300, 400, 500, 600, 
700, 800, 900, 1000), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), 
    ymax = c(863L, 0L, 2L, 0L, 0L, 0L, 0L, 0L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "wbc_max")
```

\emini


- Note that the following possible outlier values were detected: \"1.3\", \"1.6\", \"1.7\", \"1.8\", \"2.2\", \"2.5\", \"2.6\", \"28.8\", \"29.7\", \"30\" (6 additional values omitted). 



\fullline

## wbc\_mean

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             398

Median                             6.53

1st and 3rd quartiles        4.86; 8.95

Min. and max.               1.3; 207.14
---------------------------------------


\emini
\bminitwo
```{r 'Var-99-wbc-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 20, 40, 60, 80, 100, 
120, 140, 160, 180, 200), xmax = c(20, 40, 60, 80, 100, 120, 
140, 160, 180, 200, 220), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(855L, 8L, 1L, 0L, 1L, 0L, 0L, 0L, 0L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-11L)), vnam = "wbc_mean")
```

\emini


- Note that the following possible outlier values were detected: \"1.3\", \"1.43\", \"1.6\", \"1.7\", \"1.97\", \"2.1\", \"2.2\", \"22.2\", \"22.55\", \"23.3\" (6 additional values omitted). 



\fullline

## sodium\_min

\bminione

------------------------------------
Feature                       Result
------------------------- ----------
Variable type                numeric

Number of missing obs.       0 (0 %)

Number of unique values           38

Median                           138

1st and 3rd quartiles       135; 140

Min. and max.               114; 157
------------------------------------


\emini
\bminitwo
```{r 'Var-100-sodium-min', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(110L, 115L, 120L, 125L, 
130L, 135L, 140L, 145L, 150L, 155L), xmax = c(115L, 120L, 125L, 
130L, 135L, 140L, 145L, 150L, 155L, 160L), ymin = c(0, 0, 0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(1L, 2L, 9L, 34L, 208L, 413L, 171L, 
18L, 5L, 5L)), class = "data.frame", row.names = c(NA, -10L)), 
    vnam = "sodium_min")
```

\emini


- Note that the following possible outlier values were detected: \"114\", \"117\", \"120\", \"121\", \"122\", \"123\", \"124\", \"125\", \"126\", \"127\" (8 additional values omitted). 



\fullline

## sodium\_max

\bminione

------------------------------------
Feature                       Result
------------------------- ----------
Variable type                numeric

Number of missing obs.       0 (0 %)

Number of unique values           36

Median                           140

1st and 3rd quartiles       138; 143

Min. and max.               127; 168
------------------------------------


\emini
\bminitwo
```{r 'Var-101-sodium-max', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(125L, 130L, 135L, 140L, 
145L, 150L, 155L, 160L, 165L), xmax = c(130L, 135L, 140L, 145L, 
150L, 155L, 160L, 165L, 170L), ymin = c(0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(13L, 58L, 381L, 318L, 71L, 9L, 6L, 9L, 1L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "sodium_max")
```

\emini


- Note that the following possible outlier values were detected: \"127\", \"128\", \"129\", \"130\", \"131\", \"132\", \"133\", \"134\", \"158\", \"159\" (4 additional values omitted). 



\fullline

## sodium\_mean

\bminione

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                      numeric

Number of missing obs.             0 (0 %)

Number of unique values                179

Median                                 139

1st and 3rd quartiles        136.67; 141.5

Min. and max.               120.13; 160.86
------------------------------------------


\emini
\bminitwo
```{r 'Var-102-sodium-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(120L, 125L, 130L, 135L, 
140L, 145L, 150L, 155L, 160L), xmax = c(125L, 130L, 135L, 140L, 
145L, 150L, 155L, 160L, 165L), ymin = c(0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(2L, 18L, 92L, 424L, 279L, 37L, 4L, 7L, 3L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "sodium_mean")
```

\emini


- Note that the following possible outlier values were detected: \"120.13\", \"124.75\", \"125.67\", \"125.75\", \"125.86\", \"126.25\", \"126.5\", \"127\", \"127.56\", \"128\" (13 additional values omitted). 



\fullline

## potassium\_min

\bminione

------------------------------------
Feature                       Result
------------------------- ----------
Variable type                numeric

Number of missing obs.       0 (0 %)

Number of unique values           32

Median                           3.7

1st and 3rd quartiles       3.4; 4.1

Min. and max.               2.4; 5.6
------------------------------------


\emini
\bminitwo
```{r 'Var-103-potassium-min', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(2, 2.5, 3, 3.5, 4, 4.5, 
5, 5.5), xmax = c(2.5, 3, 3.5, 4, 4.5, 5, 5.5, 6), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(2L, 58L, 258L, 330L, 178L, 32L, 
7L, 1L)), class = "data.frame", row.names = c(NA, -8L)), vnam = "potassium_min")
```

\emini


- Note that the following possible outlier values were detected: \"5.2\", \"5.3\", \"5.4\", \"5.6\". 



\fullline

## potassium\_max

\bminione

------------------------------------
Feature                       Result
------------------------- ----------
Variable type                numeric

Number of missing obs.       0 (0 %)

Number of unique values           34

Median                           4.1

1st and 3rd quartiles       3.8; 4.5

Min. and max.                 3; 8.2
------------------------------------


\emini
\bminitwo
```{r 'Var-104-potassium-max', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(3, 3.5, 4, 4.5, 5, 5.5, 
6, 6.5, 7, 7.5, 8), xmax = c(3.5, 4, 4.5, 5, 5.5, 6, 6.5, 7, 
7.5, 8, 8.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(74L, 
324L, 292L, 130L, 32L, 5L, 7L, 1L, 0L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-11L)), vnam = "potassium_max")
```

\emini


- Note that the following possible outlier values were detected: \"3\", \"3.2\", \"6.2\", \"6.3\", \"6.4\", \"6.9\", \"8.2\". 



\fullline

## potassium\_mean

\bminione

-------------------------------------
Feature                        Result
------------------------- -----------
Variable type                 numeric

Number of missing obs.        0 (0 %)

Number of unique values           135

Median                            3.9

1st and 3rd quartiles       3.65; 4.2

Min. and max.                 3; 5.81
-------------------------------------


\emini
\bminitwo
```{r 'Var-105-potassium-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(3, 3.2, 3.4, 3.6, 3.8, 
4, 4.2, 4.4, 4.6, 4.8, 5, 5.2, 5.4, 5.6, 5.8), xmax = c(3.2, 
3.4, 3.6, 3.8, 4, 4.2, 4.4, 4.6, 4.8, 5, 5.2, 5.4, 5.6, 5.8, 
6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(16L, 
74L, 102L, 169L, 166L, 128L, 99L, 54L, 31L, 13L, 7L, 2L, 3L, 
1L, 1L)), class = "data.frame", row.names = c(NA, -15L)), vnam = "potassium_mean")
```

\emini


- Note that the following possible outlier values were detected: \"3\", \"3.05\", \"5.35\", \"5.47\", \"5.6\", \"5.7\", \"5.81\". 



\fullline

## creatinine\_min

\bminione

------------------------------------
Feature                       Result
------------------------- ----------
Variable type                numeric

Number of missing obs.       0 (0 %)

Number of unique values          175

Median                            68

1st and 3rd quartiles         54; 93

Min. and max.               20; 1049
------------------------------------


\emini
\bminitwo
```{r 'Var-106-creatinine-min', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 100, 200, 300, 400, 
500, 600, 700, 800, 900, 1000), xmax = c(100, 200, 300, 400, 
500, 600, 700, 800, 900, 1000, 1100), ymin = c(0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0), ymax = c(697L, 113L, 20L, 15L, 9L, 4L, 1L, 
3L, 2L, 0L, 2L)), class = "data.frame", row.names = c(NA, -11L
)), vnam = "creatinine_min")
```

\emini


- Note that the following possible outlier values were detected: \"20\", \"23\", \"24\", \"25\", \"26\", \"27\", \"29\", \"31\", \"32\", \"33\" (42 additional values omitted). 



\fullline

## creatinine\_max

\bminione

------------------------------------
Feature                       Result
------------------------- ----------
Variable type                numeric

Number of missing obs.       0 (0 %)

Number of unique values          203

Median                            79

1st and 3rd quartiles        62; 110

Min. and max.               25; 2094
------------------------------------


\emini
\bminitwo
```{r 'Var-107-creatinine-max', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 200, 400, 600, 800, 
1000, 1200, 1400, 1600, 1800, 2000), xmax = c(200, 400, 600, 
800, 1000, 1200, 1400, 1600, 1800, 2000, 2200), ymin = c(0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(784L, 45L, 16L, 6L, 8L, 
5L, 0L, 1L, 0L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-11L)), vnam = "creatinine_max")
```

\emini


- Note that the following possible outlier values were detected: \"25\", \"27\", \"29\", \"31\", \"32\", \"34\", \"35\", \"37\", \"38\", \"39\" (47 additional values omitted). 



\fullline

## creatinine\_mean

\bminione

-----------------------------------------
Feature                            Result
------------------------- ---------------
Variable type                     numeric

Number of missing obs.            0 (0 %)

Number of unique values               435

Median                              73.67

1st and 3rd quartiles       58.37; 101.25

Min. and max.                22.5; 1209.7
-----------------------------------------


\emini
\bminitwo
```{r 'Var-108-creatinine-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 100, 200, 300, 400, 
500, 600, 700, 800, 900, 1000, 1100, 1200), xmax = c(100, 200, 
300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1200, 1300), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(642L, 155L, 20L, 
17L, 10L, 6L, 4L, 5L, 2L, 1L, 2L, 1L, 1L)), class = "data.frame", row.names = c(NA, 
-13L)), vnam = "creatinine_mean")
```

\emini


- Note that the following possible outlier values were detected: \"22.5\", \"26.33\", \"28.75\", \"29\", \"29.5\", \"31\", \"31.75\", \"35\", \"35.67\", \"36\" (62 additional values omitted). 



\fullline

## eos\_min

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          41

Median                            0

1st and 3rd quartiles       0; 0.03

Min. and max.                0; 1.5
-----------------------------------


\emini
\bminitwo
```{r 'Var-109-eos-min', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.1, 0.2, 0.3, 0.4, 
0.5, 0.6, 0.7, 0.8, 0.9, 1, 1.1, 1.2, 1.3, 1.4), xmax = c(0.1, 
0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1, 1.1, 1.2, 1.3, 1.4, 
1.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), 
    ymax = c(775L, 49L, 22L, 9L, 4L, 2L, 0L, 4L, 0L, 0L, 0L, 
    0L, 0L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "eos_min")
```

\emini


- Note that the following possible outlier values were detected: \"1.5\". 



\fullline

## eos\_max

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          51

Median                         0.01

1st and 3rd quartiles        0; 0.1

Min. and max.               0; 2.22
-----------------------------------


\emini
\bminitwo
```{r 'Var-110-eos-max', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.2, 0.4, 0.6, 0.8, 
1, 1.2, 1.4, 1.6, 1.8, 2, 2.2), xmax = c(0.2, 0.4, 0.6, 0.8, 
1, 1.2, 1.4, 1.6, 1.8, 2, 2.2, 2.4), ymin = c(0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(781L, 62L, 13L, 6L, 0L, 1L, 2L, 
0L, 0L, 0L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-12L)), vnam = "eos_max")
```

\emini


- Note that the following possible outlier values were detected: \"2.22\". 



\fullline

## eos\_mean

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          45

Median                         0.01

1st and 3rd quartiles       0; 0.07

Min. and max.               0; 1.85
-----------------------------------


\emini
\bminitwo
```{r 'Var-111-eos-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.2, 0.4, 0.6, 0.8, 
1, 1.2, 1.4, 1.6, 1.8), xmax = c(0.2, 0.4, 0.6, 0.8, 1, 1.2, 
1.4, 1.6, 1.8, 2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(808L, 
41L, 10L, 5L, 1L, 0L, 0L, 0L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "eos_mean")
```

\emini


- Note that the following possible outlier values were detected: \"1.85\". 



\fullline

## lymph\_min

\bminione

-------------------------------------
Feature                        Result
------------------------- -----------
Variable type                 numeric

Number of missing obs.        0 (0 %)

Number of unique values           204

Median                            0.8

1st and 3rd quartiles       0.53; 1.2

Min. and max.                 0; 16.9
-------------------------------------


\emini
\bminitwo
```{r 'Var-112-lymph-min', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 2, 4, 6, 8, 10, 12, 
14, 16), xmax = c(2, 4, 6, 8, 10, 12, 14, 16, 18), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0), ymax = c(812L, 48L, 3L, 1L, 0L, 0L, 
1L, 0L, 1L)), class = "data.frame", row.names = c(NA, -9L)), 
    vnam = "lymph_min")
```

\emini


- Note that the following possible outlier values were detected: \"0\", \"0.08\", \"0.1\", \"3.19\", \"3.66\", \"3.69\", \"5.85\", \"6\", \"7.3\", \"12.8\" (1 additional values omitted). 



\fullline

## lymph\_max

\bminione

--------------------------------------
Feature                         Result
------------------------- ------------
Variable type                  numeric

Number of missing obs.         0 (0 %)

Number of unique values            231

Median                            1.17

1st and 3rd quartiles       0.85; 1.69

Min. and max.               0.16; 18.6
--------------------------------------


\emini
\bminitwo
```{r 'Var-113-lymph-max', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 2, 4, 6, 8, 10, 12, 
14, 16, 18), xmax = c(2, 4, 6, 8, 10, 12, 14, 16, 18, 20), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(750L, 106L, 3L, 5L, 0L, 
0L, 0L, 0L, 1L, 1L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "lymph_max")
```

\emini


- Note that the following possible outlier values were detected: \"0.16\", \"0.18\", \"0.24\", \"0.25\", \"0.28\", \"0.29\", \"0.3\", \"0.33\", \"0.34\", \"4.28\" (7 additional values omitted). 



\fullline

## lymph\_mean

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             225

Median                                1

1st and 3rd quartiles         0.71; 1.4

Min. and max.               0.11; 17.75
---------------------------------------


\emini
\bminitwo
```{r 'Var-114-lymph-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 2, 4, 6, 8, 10, 12, 
14, 16), xmax = c(2, 4, 6, 8, 10, 12, 14, 16, 18), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0), ymax = c(788L, 71L, 3L, 2L, 0L, 0L, 
0L, 1L, 1L)), class = "data.frame", row.names = c(NA, -9L)), 
    vnam = "lymph_mean")
```

\emini


- Note that the following possible outlier values were detected: \"0.11\", \"0.15\", \"0.16\", \"0.18\", \"0.19\", \"0.24\", \"0.25\", \"0.27\", \"0.28\", \"0.29\" (10 additional values omitted). 



\fullline

## neutrophil\_min

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             428

Median                             3.78

1st and 3rd quartiles          2.5; 5.7

Min. and max.               0.09; 24.69
---------------------------------------


\emini
\bminitwo
```{r 'Var-115-neutrophil-min', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 2, 4, 6, 8, 10, 12, 
14, 16, 18, 20, 22, 24), xmax = c(2, 4, 6, 8, 10, 12, 14, 16, 
18, 20, 22, 24, 26), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(125L, 370L, 182L, 106L, 41L, 21L, 14L, 3L, 0L, 
2L, 0L, 1L, 1L)), class = "data.frame", row.names = c(NA, -13L
)), vnam = "neutrophil_min")
```

\emini


- Note that the following possible outlier values were detected: \"0.09\", \"0.17\", \"0.35\", \"0.37\", \"0.39\", \"0.5\", \"0.59\", \"15.36\", \"15.4\", \"19.16\" (3 additional values omitted). 



\fullline

## neutrophil\_max

\bminione

------------------------------------
Feature                       Result
------------------------- ----------
Variable type                numeric

Number of missing obs.       0 (0 %)

Number of unique values          489

Median                           5.3

1st and 3rd quartiles       3.5; 8.3

Min. and max.               0.64; 83
------------------------------------


\emini
\bminitwo
```{r 'Var-116-neutrophil-max', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 10, 20, 30, 40, 50, 
60, 70, 80), xmax = c(10, 20, 30, 40, 50, 60, 70, 80, 90), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0), ymax = c(718L, 138L, 7L, 2L, 0L, 0L, 
0L, 0L, 1L)), class = "data.frame", row.names = c(NA, -9L)), 
    vnam = "neutrophil_max")
```

\emini


- Note that the following possible outlier values were detected: \"0.64\", \"0.68\", \"0.94\", \"0.95\", \"0.96\", \"1.08\", \"1.1\", \"1.15\", \"1.16\", \"1.19\" (4 additional values omitted). 



\fullline

## neutrophil\_mean

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             517

Median                             4.56

1st and 3rd quartiles        3.14; 6.79

Min. and max.               0.47; 28.48
---------------------------------------


\emini
\bminitwo
```{r 'Var-117-neutrophil-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 2, 4, 6, 8, 10, 12, 
14, 16, 18, 20, 22, 24, 26, 28), xmax = c(2, 4, 6, 8, 10, 12, 
14, 16, 18, 20, 22, 24, 26, 28, 30), ymin = c(0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(62L, 304L, 222L, 122L, 
74L, 39L, 16L, 16L, 5L, 2L, 0L, 1L, 1L, 1L, 1L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "neutrophil_mean")
```

\emini


- Note that the following possible outlier values were detected: \"0.47\", \"0.52\", \"0.61\", \"0.62\", \"0.94\", \"0.96\", \"0.98\", \"1.08\", \"1.1\", \"1.11\" (10 additional values omitted). 



\fullline

## mono\_min

\bminione

--------------------------------------
Feature                         Result
------------------------- ------------
Variable type                  numeric

Number of missing obs.         0 (0 %)

Number of unique values            124

Median                            0.41

1st and 3rd quartiles       0.29; 0.61

Min. and max.                  0; 2.02
--------------------------------------


\emini
\bminitwo
```{r 'Var-118-mono-min', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.2, 0.4, 0.6, 0.8, 
1, 1.2, 1.4, 1.6, 1.8, 2), xmax = c(0.2, 0.4, 0.6, 0.8, 1, 1.2, 
1.4, 1.6, 1.8, 2, 2.2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0), ymax = c(148L, 280L, 213L, 130L, 48L, 27L, 13L, 5L, 1L, 0L, 
1L)), class = "data.frame", row.names = c(NA, -11L)), vnam = "mono_min")
```

\emini


- Note that the following possible outlier values were detected: \"0\", \"0.03\", \"0.04\", \"0.05\", \"0.06\", \"0.07\", \"0.08\", \"0.09\", \"0.1\", \"0.11\" (3 additional values omitted). 



\fullline

## mono\_max

\bminione

--------------------------------------
Feature                         Result
------------------------- ------------
Variable type                  numeric

Number of missing obs.         0 (0 %)

Number of unique values            158

Median                             0.6

1st and 3rd quartiles       0.42; 0.87

Min. and max.                   0; 9.5
--------------------------------------


\emini
\bminitwo
```{r 'Var-119-mono-max', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 1, 2, 3, 4, 5, 6, 
7, 8, 9), xmax = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(726L, 129L, 8L, 2L, 0L, 
0L, 0L, 0L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "mono_max")
```

\emini


- Note that the following possible outlier values were detected: \"0\", \"0.06\", \"0.08\", \"0.1\", \"0.11\", \"0.12\", \"0.13\", \"0.14\", \"2.29\", \"2.49\" (5 additional values omitted). 



\fullline

## mono\_mean

\bminione

--------------------------------------
Feature                         Result
------------------------- ------------
Variable type                  numeric

Number of missing obs.         0 (0 %)

Number of unique values            138

Median                            0.52

1st and 3rd quartiles       0.38; 0.72

Min. and max.                  0; 4.69
--------------------------------------


\emini
\bminitwo
```{r 'Var-120-mono-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.5, 1, 1.5, 2, 2.5, 
3, 3.5, 4, 4.5), xmax = c(0.5, 1, 1.5, 2, 2.5, 3, 3.5, 4, 4.5, 
5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(425L, 363L, 
68L, 5L, 3L, 1L, 0L, 0L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "mono_mean")
```

\emini


- Note that the following possible outlier values were detected: \"0\", \"0.06\", \"0.08\", \"0.09\", \"0.1\", \"0.11\", \"0.12\", \"0.13\", \"0.14\", \"0.15\" (6 additional values omitted). 



\fullline

## baso\_min

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          14

Median                            0

1st and 3rd quartiles       0; 0.01

Min. and max.               0; 0.16
-----------------------------------


\emini
\bminitwo
```{r 'Var-121-baso-min', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.02, 0.04, 0.06, 
0.08, 0.1, 0.12, 0.14), xmax = c(0.02, 0.04, 0.06, 0.08, 0.1, 
0.12, 0.14, 0.16), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(804L, 
46L, 5L, 3L, 5L, 1L, 0L, 2L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "baso_min")
```

\emini




\fullline

## baso\_max

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          25

Median                         0.01

1st and 3rd quartiles       0; 0.02

Min. and max.                  0; 1
-----------------------------------


\emini
\bminitwo
```{r 'Var-122-baso-max', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.1, 0.2, 0.3, 0.4, 
0.5, 0.6, 0.7, 0.8, 0.9), xmax = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 
0.7, 0.8, 0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(849L, 
9L, 3L, 1L, 1L, 2L, 0L, 0L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "baso_max")
```

\emini


- Note that the following possible outlier values were detected: \"0.11\", \"0.12\", \"0.14\", \"0.15\", \"0.16\", \"0.19\", \"0.23\", \"0.25\", \"0.27\", \"0.37\" (4 additional values omitted). 



\fullline

## baso\_mean

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          19

Median                         0.01

1st and 3rd quartiles       0; 0.02

Min. and max.               0; 0.33
-----------------------------------


\emini
\bminitwo
```{r 'Var-123-baso-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.05, 0.1, 0.15, 
0.2, 0.25, 0.3), xmax = c(0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35
), ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(838L, 19L, 3L, 1L, 
2L, 1L, 2L)), class = "data.frame", row.names = c(NA, -7L)), 
    vnam = "baso_mean")
```

\emini


- Note that the following possible outlier values were detected: \"0.06\", \"0.07\", \"0.08\", \"0.09\", \"0.1\", \"0.11\", \"0.13\", \"0.16\", \"0.21\", \"0.25\" (3 additional values omitted). 



\fullline

## sbp\_min

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values              93

Median                              110

1st and 3rd quartiles       100.25; 121

Min. and max.                   11; 173
---------------------------------------


\emini
\bminitwo
```{r 'Var-124-sbp-min', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 20, 40, 60, 80, 100, 
120, 140, 160), xmax = c(20, 40, 60, 80, 100, 120, 140, 160, 
180), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(8L, 0L, 4L, 
30L, 175L, 430L, 177L, 36L, 6L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "sbp_min")
```

\emini


- Note that the following possible outlier values were detected: \"11\", \"12\", \"16\", \"19\", \"54\", \"60\", \"62\", \"65\", \"66\", \"69\" (10 additional values omitted). 



\fullline

## sbp\_max

\bminione

------------------------------------
Feature                       Result
------------------------- ----------
Variable type                numeric

Number of missing obs.       0 (0 %)

Number of unique values          117

Median                           148

1st and 3rd quartiles       133; 164

Min. and max.                96; 224
------------------------------------


\emini
\bminitwo
```{r 'Var-125-sbp-max', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(90L, 100L, 110L, 120L, 
130L, 140L, 150L, 160L, 170L, 180L, 190L, 200L, 210L, 220L), 
    xmax = c(100L, 110L, 120L, 130L, 140L, 150L, 160L, 170L, 
    180L, 190L, 200L, 210L, 220L, 230L), ymin = c(0, 0, 0, 0, 
    0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(4L, 15L, 47L, 119L, 
    151L, 138L, 134L, 109L, 73L, 37L, 14L, 15L, 6L, 4L)), class = "data.frame", row.names = c(NA, 
-14L)), vnam = "sbp_max")
```

\emini


- Note that the following possible outlier values were detected: \"219\", \"220\", \"221\", \"223\", \"224\". 



\fullline

## sbp\_mean

\bminione

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                      numeric

Number of missing obs.             0 (0 %)

Number of unique values                637

Median                                 127

1st and 3rd quartiles       117.69; 140.21

Min. and max.                86.83; 188.27
------------------------------------------


\emini
\bminitwo
```{r 'Var-126-sbp-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(80L, 90L, 100L, 110L, 
120L, 130L, 140L, 150L, 160L, 170L, 180L), xmax = c(90L, 100L, 
110L, 120L, 130L, 140L, 150L, 160L, 170L, 180L, 190L), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(5L, 17L, 71L, 172L, 222L, 
161L, 103L, 80L, 19L, 14L, 2L)), class = "data.frame", row.names = c(NA, 
-11L)), vnam = "sbp_mean")
```

\emini


- Note that the following possible outlier values were detected: \"86.83\", \"87.88\", \"89\", \"89.13\", \"92.4\", \"95.17\", \"96\", \"96.2\", \"96.63\", \"97.8\" (14 additional values omitted). 



\fullline

## dbp\_min

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          60

Median                           60

1st and 3rd quartiles        54; 67

Min. and max.                 6; 93
-----------------------------------


\emini
\bminitwo
```{r 'Var-127-dbp-min', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 10, 20, 30, 40, 50, 
60, 70, 80, 90), xmax = c(10, 20, 30, 40, 50, 60, 70, 80, 90, 
100), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1L, 0L, 
4L, 27L, 108L, 308L, 288L, 112L, 16L, 2L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "dbp_min")
```

\emini


- Note that the following possible outlier values were detected: \"6\", \"24\", \"28\", \"30\", \"34\", \"87\", \"89\", \"91\", \"93\". 



\fullline

## dbp\_max

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          76

Median                           83

1st and 3rd quartiles        77; 90

Min. and max.               55; 811
-----------------------------------


\emini
\bminitwo
```{r 'Var-128-dbp-max', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(50L, 100L, 150L, 200L, 
250L, 300L, 350L, 400L, 450L, 500L, 550L, 600L, 650L, 700L, 750L, 
800L), xmax = c(100L, 150L, 200L, 250L, 300L, 350L, 400L, 450L, 
500L, 550L, 600L, 650L, 700L, 750L, 800L, 850L), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(802L, 
57L, 1L, 0L, 0L, 0L, 0L, 0L, 0L, 1L, 1L, 1L, 1L, 0L, 1L, 1L)), class = "data.frame", row.names = c(NA, 
-16L)), vnam = "dbp_max")
```

\emini


- Note that the following possible outlier values were detected: \"55\", \"56\", \"59\", \"60\", \"61\", \"62\", \"63\", \"116\", \"117\", \"118\" (15 additional values omitted). 



\fullline

## dbp\_mean

\bminione

-----------------------------------------
Feature                            Result
------------------------- ---------------
Variable type                     numeric

Number of missing obs.            0 (0 %)

Number of unique values               555

Median                              71.67

1st and 3rd quartiles           66; 77.14

Min. and max.               48.19; 128.13
-----------------------------------------


\emini
\bminitwo
```{r 'Var-129-dbp-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(40L, 50L, 60L, 70L, 
80L, 90L, 100L, 110L, 120L), xmax = c(50L, 60L, 70L, 80L, 90L, 
100L, 110L, 120L, 130L), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), 
    ymax = c(2L, 60L, 307L, 361L, 118L, 11L, 5L, 1L, 1L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "dbp_mean")
```

\emini


- Note that the following possible outlier values were detected: \"48.19\", \"96.1\", \"99.1\", \"99.2\", \"101.27\", \"101.75\", \"103.67\", \"103.88\", \"110\", \"113.05\" (1 additional values omitted). 



\fullline

## temp\_min

\bminione

--------------------------------------
Feature                         Result
------------------------- ------------
Variable type                  numeric

Number of missing obs.         0 (0 %)

Number of unique values             36

Median                            36.3

1st and 3rd quartiles       35.9; 36.6

Min. and max.                 34; 39.3
--------------------------------------


\emini
\bminitwo
```{r 'Var-130-temp-min', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(34, 34.5, 35, 35.5, 
36, 36.5, 37, 37.5, 38, 38.5, 39), xmax = c(34.5, 35, 35.5, 36, 
36.5, 37, 37.5, 38, 38.5, 39, 39.5), ymin = c(0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0), ymax = c(15L, 40L, 71L, 195L, 312L, 217L, 
13L, 2L, 0L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-11L)), vnam = "temp_min")
```

\emini


- Note that the following possible outlier values were detected: \"37.1\", \"37.2\", \"37.3\", \"37.4\", \"37.5\", \"37.6\", \"39.3\". 



\fullline

## temp\_max

\bminione

------------------------------------
Feature                       Result
------------------------- ----------
Variable type                numeric

Number of missing obs.       0 (0 %)

Number of unique values           51

Median                          37.4

1st and 3rd quartiles       37; 38.2

Min. and max.               34; 40.7
------------------------------------


\emini
\bminitwo
```{r 'Var-131-temp-max', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(34, 34.5, 35, 35.5, 
36, 36.5, 37, 37.5, 38, 38.5, 39, 39.5, 40, 40.5), xmax = c(34.5, 
35, 35.5, 36, 36.5, 37, 37.5, 38, 38.5, 39, 39.5, 40, 40.5, 41
), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1L, 
0L, 2L, 9L, 47L, 242L, 184L, 125L, 96L, 70L, 64L, 20L, 5L, 1L
)), class = "data.frame", row.names = c(NA, -14L)), vnam = "temp_max")
```

\emini


- Note that the following possible outlier values were detected: \"34\", \"35.3\", \"35.4\", \"35.6\", \"35.8\", \"35.9\", \"36\", \"36.1\", \"36.2\", \"36.3\" (2 additional values omitted). 



\fullline

## temp\_mean

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              225

Median                             36.84

1st and 3rd quartiles       36.53; 37.15

Min. and max.                   34; 39.3
----------------------------------------


\emini
\bminitwo
```{r 'Var-132-temp-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(34, 34.5, 35, 35.5, 
36, 36.5, 37, 37.5, 38, 38.5, 39), xmax = c(34.5, 35, 35.5, 36, 
36.5, 37, 37.5, 38, 38.5, 39, 39.5), ymin = c(0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0), ymax = c(1L, 0L, 7L, 35L, 163L, 370L, 196L, 
53L, 34L, 6L, 1L)), class = "data.frame", row.names = c(NA, -11L
)), vnam = "temp_mean")
```

\emini


- Note that the following possible outlier values were detected: \"34\", \"35.25\", \"35.33\", \"35.38\", \"35.4\", \"35.43\", \"35.45\", \"35.5\", \"35.53\", \"35.57\" (22 additional values omitted). 



\fullline

## so2\_min

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          40

Median                           92

1st and 3rd quartiles        88; 94

Min. and max.               41; 100
-----------------------------------


\emini
\bminitwo
```{r 'Var-133-so2-min', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(40L, 45L, 50L, 55L, 
60L, 65L, 70L, 75L, 80L, 85L, 90L, 95L), xmax = c(45L, 50L, 55L, 
60L, 65L, 70L, 75L, 80L, 85L, 90L, 95L, 100L), ymin = c(0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(2L, 0L, 1L, 20L, 6L, 
6L, 12L, 24L, 59L, 198L, 409L, 129L)), class = "data.frame", row.names = c(NA, 
-12L)), vnam = "so2_min")
```

\emini


- Note that the following possible outlier values were detected: \"41\", \"54\", \"59\", \"60\", \"61\", \"62\", \"63\", \"97\", \"98\", \"99\" (1 additional values omitted). 



\fullline

## so2\_max

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          11

Median                           98

1st and 3rd quartiles        97; 99

Min. and max.               88; 100
-----------------------------------


\emini
\bminitwo
```{r 'Var-134-so2-max', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = 88:99, xmax = 89:100, 
    ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1L, 
    1L, 0L, 8L, 5L, 31L, 44L, 102L, 143L, 171L, 159L, 201L)), class = "data.frame", row.names = c(NA, 
-12L)), vnam = "so2_max")
```

\emini


- Note that the following possible outlier values were detected: \"88\", \"90\", \"92\", \"93\". 



\fullline

## so2\_mean

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              451

Median                                95

1st and 3rd quartiles       93.52; 96.67

Min. and max.                    25; 100
----------------------------------------


\emini
\bminitwo
```{r 'Var-135-so2-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(25L, 30L, 35L, 40L, 
45L, 50L, 55L, 60L, 65L, 70L, 75L, 80L, 85L, 90L, 95L), xmax = c(30L, 
35L, 40L, 45L, 50L, 55L, 60L, 65L, 70L, 75L, 80L, 85L, 90L, 95L, 
100L), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), 
    ymax = c(7L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 5L, 
    22L, 405L, 427L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "so2_mean")
```

\emini


- Note that the following possible outlier values were detected: \"25\", \"81.07\", \"81.33\", \"83.17\", \"84.29\", \"84.46\", \"85.57\", \"86.06\", \"86.89\", \"88\" (6 additional values omitted). 



\fullline

## rr\_min

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          17

Median                           18

1st and 3rd quartiles        17; 20

Min. and max.                 8; 32
-----------------------------------


\emini
\bminitwo
```{r 'Var-136-rr-min', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(8L, 10L, 12L, 14L, 16L, 
18L, 20L, 22L, 24L, 26L, 28L, 30L), xmax = c(10L, 12L, 14L, 16L, 
18L, 20L, 22L, 24L, 26L, 28L, 30L, 32L), ymin = c(0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0), ymax = c(12L, 4L, 6L, 192L, 404L, 223L, 
10L, 11L, 1L, 0L, 2L, 1L)), class = "data.frame", row.names = c(NA, 
-12L)), vnam = "rr_min")
```

\emini


- Note that the following possible outlier values were detected: \"8\", \"9\", \"10\", \"12\", \"26\", \"30\", \"32\". 



\fullline

## rr\_max

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          27

Median                           22

1st and 3rd quartiles        20; 26

Min. and max.                16; 50
-----------------------------------


\emini
\bminitwo
```{r 'Var-137-rr-max', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(15L, 20L, 25L, 30L, 
35L, 40L, 45L), xmax = c(20L, 25L, 30L, 35L, 40L, 45L, 50L), 
    ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(368L, 276L, 112L, 
    46L, 41L, 8L, 15L)), class = "data.frame", row.names = c(NA, 
-7L)), vnam = "rr_max")
```

\emini


- Note that the following possible outlier values were detected: \"16\". 



\fullline

## rr\_mean

\bminione

-------------------------------------
Feature                        Result
------------------------- -----------
Variable type                 numeric

Number of missing obs.        0 (0 %)

Number of unique values           302

Median                          19.97

1st and 3rd quartiles       19; 21.16

Min. and max.               14.57; 40
-------------------------------------


\emini
\bminitwo
```{r 'Var-138-rr-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(14L, 16L, 18L, 20L, 
22L, 24L, 26L, 28L, 30L, 32L, 34L, 36L, 38L), xmax = c(16L, 18L, 
20L, 22L, 24L, 26L, 28L, 30L, 32L, 34L, 36L, 38L, 40L), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(6L, 63L, 441L, 
223L, 68L, 23L, 19L, 11L, 6L, 3L, 0L, 0L, 3L)), class = "data.frame", row.names = c(NA, 
-13L)), vnam = "rr_mean")
```

\emini


- Note that the following possible outlier values were detected: \"14.57\", \"15.67\", \"15.8\", \"16\", \"16.67\", \"16.73\", \"16.75\", \"16.8\", \"16.86\", \"25.78\" (37 additional values omitted). 



\fullline

## fio2\_min

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          39

Median                           21

1st and 3rd quartiles        21; 21

Min. and max.               21; 100
-----------------------------------


\emini
\bminitwo
```{r 'Var-139-fio2-min', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(20L, 30L, 40L, 50L, 
60L, 70L, 80L, 90L), xmax = c(30L, 40L, 50L, 60L, 70L, 80L, 90L, 
100L), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(723L, 51L, 
29L, 14L, 6L, 3L, 11L, 29L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "fio2_min")
```

\emini


- Note that the following possible outlier values were detected: \"22\", \"24\", \"26\", \"28\", \"30\", \"31\", \"32\", \"34\", \"35\", \"36\" (28 additional values omitted). 



\fullline

## fio2\_max

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          36

Median                           40

1st and 3rd quartiles        24; 50

Min. and max.               21; 100
-----------------------------------


\emini
\bminitwo
```{r 'Var-140-fio2-max', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(20L, 30L, 40L, 50L, 
60L, 70L, 80L, 90L), xmax = c(30L, 40L, 50L, 60L, 70L, 80L, 90L, 
100L), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(276L, 365L, 
11L, 19L, 16L, 6L, 11L, 162L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "fio2_max")
```

\emini




\fullline

## fio2\_mean

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             257

Median                               25

1st and 3rd quartiles       21.6; 35.05

Min. and max.                   21; 100
---------------------------------------


\emini
\bminitwo
```{r 'Var-141-fio2-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(20L, 30L, 40L, 50L, 
60L, 70L, 80L, 90L), xmax = c(30L, 40L, 50L, 60L, 70L, 80L, 90L, 
100L), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(626L, 40L, 
52L, 33L, 33L, 18L, 21L, 43L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "fio2_mean")
```

\emini




\fullline

## mv

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-142-mv', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(800L, 66L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "mv")
```

\emini




\fullline

## icu

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-143-icu', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(716L, 150L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "icu")
```

\emini




\fullline

## levelofcare

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "1"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-144-levelofcare', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(81L, 785L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "levelofcare")
```

\emini




\fullline

## wave

* Note that this variable is treated as a factor variable below, as it only takes a few unique values.

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "1"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-145-wave', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(422L, 444L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "wave")
```

\emini




\fullline



Report generation information:

 *  Created by: Eric Yamga (username: `eyamga`).

 *  Report creation time: Tue Feb 02 2021 18:35:38

 *  Report was run from directory: `/Users/eyamga/Documents/Medecine/Recherche/CODA19/git/CODA19-Phenotyper/r_eyamga`

 *  dataMaid v1.4.0 [Pkg: 2019-12-10 from CRAN (R 4.0.2)]

 *  R version 4.0.3 (2020-10-10).

 *  Platform: x86_64-apple-darwin17.0 (64-bit)(macOS Catalina 10.15.7).

 *  Function call: `dataMaid::makeDataReport(data = covid24h_imputed, render = FALSE, 
    file = "coda19CHUM24h_imputed.rmd", replace = TRUE)`

